\section*{\centering{Publications}}
\label{sec:pubs}

\subsection*{Papers}

\subsubsection*{Published}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Henderson, J. M., \& Ferreira, F. (2022). Visual attention during seeing for speaking in healthy aging. \textit{Psychology and Aging}. Advance online publication. PsyArXiv preprint: \url{https://psyarxiv.com/6qt9p/}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Barker, M., Peacock, C. E., Hayes, T. R., Henderson, J. M., \& Ferreira, F. (2022). Look at what I can do: Object affordances guide visual attention while speakers describe potential actions. \textit{Attention, Perception, \& Psychophysics}. DOI: https://doi.org/10.3758/s13414-022-02467-6. PsyArXiv preprint: \url{https://psyarxiv.com/fna9z}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Cheng, M., McMahan, B. C., \& Shome, R. (2021). Why are the batteries in the microwave?: Use of semantic information under uncertainty in a search task. \textit{Cognitive Research: Principles and Implications, 6}, 32. \url{https://cognitiveresearchjournal.springeropen.com/articles/10.1186/s41235-021-00294-1}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Cullimore, R. A., Henderson, J. M., \& Ferreira, F. (2021). When more is more: Redundant modifiers can facilitate visual search. \textit{Cognitive Research: Principles and Implications, 6}, 10. \url{https://cognitiveresearchjournal.springeropen.com/articles/10.1186/s41235-021-00275-4}

\hangpara{.45in}{1}Beier, E. J., Chantavarin, S., \textbf{Rehrig, G.}, Ferreira, F., \& Miller, L. M. (2021). Cortical tracking of speech: Towards collaboration between the fields of signal and sentence processing. \textit{Journal of Cognitive Neuroscience, 33}(4), 574-593. \url{https://www.mitpressjournals.org/doi/abs/10.1162/jocn_a_01676}.

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Henderson, J. M., \& Ferreira, F. (2020). When scenes speak louder than words: Language does not mediate the relationship between scene meaning and visual attention. \textit{Memory \& Cognition, 48}(7), 1181-1195. PsyArXiv preprint: \url{https://psyarxiv.com/3h7au/}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Peacock, C. E., Hayes, T. R., Henderson, J. M., \& Ferreira, F. (2020). Where the action could be: Speakers look at graspable objects and meaningful scene regions when describing potential actions. \textit{Journal of Experimental Psychology: Language, Memory, and Cognition, 46}(9), 1659-1681. PsyArXiv preprint: \url{https://psyarxiv.com/6uep5/}

\hangpara{.45in}{1}Henderson, J. M., Hayes, T. R., Peacock, C. E., \& \textbf{Rehrig, G.}. (2019). Meaning and attentional guidance in scenes: A review of the meaning map approach. \textit{Vision, 3}(2), 19.


\hangpara{.45in}{1}Ferreira,F., \& \textbf{Rehrig, G.}. (2019). Linearisation during language production: evidence from scene meaning and saliency maps. \textit{Language, Cognition and Neuroscience,} 1-11.


\hangpara{.45in}{1}Henderson, J. M., Hayes, T. R., \textbf{Rehrig, G.}, \& Ferreira, F. (2018). Meaning guides attention during real-world scene description. \textit{Scientific Reports, 8,} 13504. 


\hangpara{.45in}{1}\textbf{Rehrig, G.}, \& Stromswold, K. (2018). What does the DAP:IQ measure?: Drawing comparisons between drawing performance and developmental assessments. \textit{The Journal of Genetic Psychology,179}(1), 9-18.


\hangpara{.45in}{1}Torres, E. B., Isenhower, R. W., Yanovich, P., \textbf{Rehrig, G.}, Stigler, K., Nurnberger, J., \& Jos\'e, J. V. (2013). Strategies to develop putative biomarkers to characterize the female phenotype with autism spectrum disorders. \textit{Journal of Neurophysiology, 110}(7), 1646-1662.

%\subsubsection*{Accepted}

%\subsubsection*{Under Revision}

%\subsubsection*{Under Review}

%\subsubsection*{Submitted}

%\subsubsection*{In Preparation}

\subsection*{Conference Presentations}

\subsubsection*{Talks}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Peacock, C. E., Henderson, J. M., Ferreira, F. (2019). But what does it mean?: Meaning and language in real-world scene processing. May 24th 2019, \textit{Spring Psychology Conference}, Center for Mind and Brain, Davis, CA.


\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Henderson, J. M., Ferreira, F. (2018). If you see something, say something: Meaning guides visual attention during the description of rich scenes. May 4th 2018, \textit{Spring Psychology Conference}, Center for Mind and Brain, Davis, CA.


\hangpara{.45in}{1}\textbf{Rehrig, G.}, Schrum, N., Stromswold, K. (2017). Acoustic correlates of syntax in English sentences produced by Mandarin speakers. December 2nd 2017, \textit{California Meeting on Psycholinguistics}, UCLA, Los Angeles, CA.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Abraham, C., Patel, C., Stromswold, K. (2015). Children's human figure drawing tasks: Measures of intelligence or motor skills? March 7th 2015, \textit{Eastern Psychological Association Conference}, Philadelphia Marriott Downtown, Philadelphia, PA.



\hangpara{.45in}{1}\textbf{Johnson, G.}\footnote{Author \textbf{Johnson, G.} is author \textbf{Rehrig, G.} with a previous last name.} (2011). Action packed: Applying semantic blocking to reveal the structure of action knowledge.  April 16th 2011, \textit{26th Annual Undergraduate Student Psychology Conference}, Lehigh Valley Association of Independent Colleges, Lafayette College, Easton, PA.

\subsubsection*{Posters}

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Barker, M., Cotter, B., Liu, Z., Qiu, H. \& Ferreira, F. (2022). Trade-offs between memory retrieval and planning in language production. Poster presentation given virtually on March 24th, 2022 at the 35th Annual Conference on Human Sentence Processing, hosted by the University of California, Santa Cruz, Santa Cruz, CA.

\hangpara{.45in}{1}\textbf{Rehrig, G.}, \& Ferreira, F. (2021). Good-enough for all intensive purposes: Eggcorns and noisy channel processing. Short presentation given virtually on March 4th, 2021 at the 34th Annual CUNY Conference on Human Sentence Processing, University of Pennsylvania, Philadelphia, PA. Presentation files available on the OSF: \url{https://osf.io/26fnv/}. 

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T., Henderson, J. M., \& Ferreira, F. (2020). Visual attention during seeing for speaking in healthy aging. Poster presented at the Annual Meeting of the Psychonomic Society, November 21, 2020. Poster file available on the OSF: \url{https://osf.io/shdbz/}. 

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Peacock, C. E., Hayes, T. R., Henderson, J. M. \& Ferreira, F. (2020). Where the action could be: Speakers look at graspable objects and meaningful scene regions when describing potential actions. Poster presented on June 19th, 2020, V-VSS 2020. Video presentation, poster file, and preprint for our related published manuscript available on the OSF: \url{https://osf.io/s5anf/}.

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Henderson, J. M. \& Ferreira, F. (2020). Setting the scene: Saliency and meaning in linearization during scene description. Poster presented on March 20th, 2020 at the 33rd Annual CUNY Human Sentence Processing Conference, University of Massachusetts, Amherst. Video presentation and related files available on the OSF: \url{https://osf.io/hp7k8/}.

\hangpara{.45in}{1}\textbf{Rehrig, G.}, Hayes, T. R., Henderson, J. M. \& Ferreira, F. (2018). If you see something, say something: Meaning guides visual attention during the description of rich scenes. Poster presented at the \textit{Annual Meeting of the Psychonomic Society}, New Orleans, LA, November 17, 2018.


\hangpara{.45in}{1}\textbf{Rehrig, G.}, Schrum, N., Knutsen, S., Stromswold, K. (2017). Use it or lose it: Delayed syntactic integration in L2 English speakers. Poster presented March 17th 2018, \textit{The 31st Annual CUNY Conference on Human Sentence Processing}, UC Davis Conference Center, Davis, CA.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Knutsen, S., Schrum, N., de Lacy, P., Stromswold, K. (2017). The long and short of it: The role of verb stem vowel duration in sentence processing. Poster presented July  2017, \textit{The 39th Annual Meeting of the Cognitive Science Society}, Hilton London Metropole, London, UK.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Cheng, M., McMahan, B. C., Shome, R. (2016). Why are the batteries in the microwave?: Use of semantic information under uncertainty in a search task. Poster presented May 17th 2016, \textit{Vision Sciences Society}, TradeWinds Island Resort, St. Pete Beach, FL.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Abraham, C., Patel, C., Stromswold, K. (2015). Components of drawing ability: A cross-sectional study. Poster presented March 20th 2015, \textit{2015 Society for Research in Child Development Biennial Meeting}, Pennsylvania Convention Center, Philadelphia, PA.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Beier, E., Chalmers, E., Schrum, N., Stromswold, K. (2015). Robust acoustic cues indicate upcoming structure in active and passive sentences. Poster presented March 19th 2015, \textit{The 28th Annual CUNY Conference on Human Sentence Processing}, Midtown Los Angeles Radisson Hotel, Los Angeles, CA.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Beier, E., Chalmers, E., Schrum, N., Stromswold, K. (2015). Acoustic correlates of future syntactic structure in active and passive sentences. Poster presented March 7th 2015, \textit{Eastern Psychological Association Conference}, Philadelphia Marriott Downtown, Philadelphia, PA.



\hangpara{.45in}{1}\textbf{Rehrig, G.}, Yanovich, P., DiFeo, G., Yang, L., Santos, E. M., Ross, N., Torres, E. B. (2012). Congruent map between the kinesthetic and the visual perceptions of our physical movements, even with noise. October 17th 2012, \textit{Society for Neuroscience Conference}, Ernest N. Morial Convention Center, New Orleans, LA.



\hangpara{.45in}{1}\textbf{Johnson, G.}, Yanovich, P., DiFeo, G., Yang, L., Santos, E. M., Ross, N., Torres, E. B. (2012). What do we see in each other: How movement drives social interaction. May 31st, 2012, \textit{National Science Foundation IGERT PI Meeting}, Capitol Hilton, Washington, D.C.



\hangpara{.45in}{1}\textbf{Johnson, G.}, O'S\'eaghdha, P. (2011). Categorical and noncategorical perception of motion. March 11, 2011, Eastern Psychological Association Conference, Hyatt Regency, Cambridge, MA.



\hangpara{.45in}{1}\textbf{Johnson, G.} (2011). The notions of motions. March 29, 2011, \textit{Biennial Academic Symposium}, Lehigh University, Bethlehem, PA.



\hangpara{.45in}{1}Anderson, M., Huttle, A., \textbf{Johnson, G.}\footnote{All authors contributed equally to the project; ordering is alphabetical.} (2010). Does syllable variation affect speech preparation? April 29th 2010, \textit{College of Arts and Scienes Undergraduate Research Symposium}, Lehigh University, Bethlehem, PA.

\subsection*{Invited Talks}

\hangpara{.45in}{1}Acoustic correlates of syntax in sentence production and comprehension. Northwestern University, May 15th, 2017.